Scaffolder - Software for Microbial Genome Scaffolding.

### 2011-02-09 text/src/article.tex
Remove numbering from sections
Revise implementation

Scaffolder is written in the Ruby programming language, version 1.8.7
\cite{ruby-lang}. Unit tests were implemented during development to maintain
functionality of individual elements of source code. Integration tests were
also written to test the scaffold software interface as a whole. These unit and
integration tests were written using the RSpec and Cucumber libraries
respectively\cite{rspec}.\pb

The Scaffolder source code is documented using the Yard library\cite{yard}.
Unix manual pages for the command line interface were generated using the Ronn
library\cite{ronn}. The manipulation of biological sequences in Scaffolder is
performed using the BioRuby library\cite{bioruby}. A full list of the software
dependencies in scaffolder can be found in the Gemfile in the root of source
code directory.\pb

@@

The choice of nucleotide sequences comprising the genome scaffold is specified
in YAML \cite{yaml}. YAML is a language format for data using white-space and
indentation to produce a machine readable structure. As a standardised data
format third-party developers have the option to generate a genome scaffold
using any programming language for which a YAML parser exists. Furthermore YAML
formatted scaffold files can be validated using third party tools such as
Kwalify\cite{kwalify}.\pb

The initial assembly of sequencing reads may result in an incomplete genome
build. Comparison of contigs to reference genomes and the generation of
additional sequence from PCR translates to genome finishing as an ongoing
process. Therefore the scaffold file should be simple to edit manually in
addition to being computationally tractable. This requirement for the scaffold
files to be modifiable in a simple simple text editor is the second reason YAML
was selected as the format for scaffold files.\pb

The form of the scaffold file is a list of entries. Each entry corresponds to
a length of sequence in the the draft genome sequence. When generating the
genome sequence from the scaffold file each entry is processed in order. Each
of the nucleotide sequence specified by the scaffold file entries are
concatenated together to produce the draft genome sequence. Each entry in the
scaffold file may have attributes that define whether a sub-sequence or the
reverse complement of the sequence should be used. The types of attributes are
outlined in the Results and Discussion section below.\pb

@@

\subsubsection{Simple to use}

@@

\subsubsection{Reproducible genome construction}

@@

  \begin{description}
    \item[YAML:] YAML Ain't Markup Language\cite{yaml}
  \end{description}

>>>>

Scaffolder is written in the Ruby programming language, version 1.8.7
\cite{ruby-lang}. The scaffolder package is split into two libraries. The first
called ``scaffolder'' contains the core scaffolder application programming
interface (API). The second library ``scaffolder-tools'' contains the
scaffolder command line interface (CLI). \pb

Unit tests were implemented to develop and maintain individual elements of the
source code.  Integration tests were written to test the scaffolder software
interface as a whole. Unit tests were written using the Shoulda and RSpec
\cite{rspec} libraries.  Integration tests were written using the Cucumber
library \cite{rspec}. \pb

The Scaffolder source code is documented using the Yard library \cite{yard}.
Unix manual pages for the command line interface were generated using the Ronn
library \cite{ronn}. The manipulation of biological sequences in Scaffolder is
performed using the BioRuby library \cite{goto2010}. A full list of the
software dependencies in scaffolder can be found in the Gemfile in the root of
each source code directory.\pb

@@

The choice of nucleotide sequences making up the scaffold is specified using
the YAML syntax \cite{yaml}. YAML is a language format using whitespace and
indentation to produce a machine readable structure. As YAML is a standardised
data format, third-party developers have the option to generate a genome
scaffold using any programming language for which a YAML parser and generator
exists. The YAML website lists parsers for languages including C/C++, Ruby,
Python, Java, Perl, C\#/.NET, PHP, and JavaScript. In addition to being widely
supported YAML formatted scaffold files can be validated for correct syntax
using third party tools such as Kwalify \cite{kwalify}. \pb

As described in the Background section, the initial sequencing data assembly
may result in an incomplete genome build. The use of computational software and
generation of additional sequence using PCR translates into genome scaffolding
as an on-going process. Therefore the scaffold file should be simple to edit
update with new sequence manually in addition to being computationally
tractable. This requirement was therefore second reason YAML was selected,
where YAML is human-readable and should be relatively easy to update in a
standard text editor. \pb

The scaffold file takes the form of a list of entries. Each entry corresponds
to a region of sequence, most likely a contig, in the genome scaffold. The
scaffolder software processes this list of entries in order, converting each to
the corresponding nucleotide sequence. These nucleotide sequences are then
concatenated together to produce the draft genome sequence. Each entry in the
scaffold file may have attributes that define whether a sub-sequence or the
reverse complement of the sequence should be used. The types of attributes
available and an example scaffold file are outlined in the Results and
Discussion section below.  \pb

@@

\subsubsection*{Simple to use}

@@

\subsubsection*{Reproducible genome construction}

@@

  \begin{description}
    \item[API:] Application programming interface
    \item[CLI:] Command line interface
    \item[YAML:] YAML Ain't Markup Language\cite{yaml}
  \end{description}
